% This section is REQUIRED. Put the publications you based your chapters on here. You also need to put who did what (although almost no-one seems to actually do this...).

\chapter{List of publications}

\section*{As part of this thesis}

% The following is to get the colours to match the chapter styles
\pgfmathsetmacro\chapclrthree{\colourarray[3]}
\pgfmathsetmacro\chapclrfour{\colourarray[4]}
\pgfmathsetmacro\chapclrfive{\colourarray[5]}
\pgfmathsetmacro\chapclrsix{\colourarray[6]}

{ \small
\begin{description}
	\item[\textcolor{\chapclrthree}{Chapter \ref{ch:pfff}}:] P.J.M. Swinkels, S.G. Stuij, Z. Gong, H. Jonas, N. Ruffino, B. van der Linden, P.G. Bolhuis, S. Sacanna, S. Woutersen \& P. Schall. ``Revealing pseudorotation and ring-opening reactions in colloidal organic molecules''. In: \textit{Nature Communications}, 12, 2810 (2021). \texttt{DOI: \href{https://doi.org/10.1038/s41467-021-23144-6}{10.1038/s41467-021-23144-6}\allowbreak}.\\
	P.J.M.S., S.G.S., S.W., and P.S. conceived the study. P.J.M.S. performed the experiments with help of N.R. and B.vdL.. P.J.M.S analysed the data with help of N.R.. H.J. and P.G.B. performed the simulations. Z.G. and S.S. made the particles. P.J.M.S. and P.S. wrote the manuscript. All authors discussed the data and reviewed the manuscript. 
	\item [\textcolor{\chapclrfour}{Chapter \ref{ch:anothe-name}}:] P.J.M. Swinkels, Z. Gong, S. Sacanna, E. Noya \& P. Schall. ``Revealing defect dynamics in colloidal graphene''. \textit{Under review}.\\
	P.J.M.S. and P.S conceived the study. P.J.M.S. performed the experiments and analyzed the data. Z.G. and S.S. made the particles. P.J.M.S. and P.S. wrote the manuscript. All authors discussed the data and reviewed the manuscript.
	\item [\textcolor{\chapclrfive}{Chapter \ref{ch:name}}:] P.J.M. Swinkels, Z. Gong, S. Sacanna, E. Noya \& P. Schall. ``Pha\-ses of sur\-fa\-ce\--con\-fi\-ned
	trivalent particles''. \textit{In preparation}.\\
	P.J.M.S. and P.S. conceived the study. P.J.M.S. performed the experiments and analyzed the data. Z.G. and S.S. made the particles. E.N. performed the simulations and their analysis. P.J.M.S. and P.S. wrote the manuscript. All authors discussed the data.
	\item [\textcolor{\chapclrsix}{Chapter \ref{ch:ch6}}:]  P.J.M. Swinkels, etc., you get the idea.
\end{description}
}

\clearpage

\section*{Outside of this work}
{ \small
\begin{itemize}
	\item B. Gabryelczyk, H. Cai, X. Shi, Y. Sun, P.J.M. Swinkels, S.Salentinig, K. Pervushin \& A. Miserez. ``Hydrogen bond guidance and aromatic stacking drive li\-quid\--li\-quid phase separation of intrinsically disordered histidine-rich peptides''. In: \textit{Nature Communications}, 10, 5465 (2019). \texttt{DOI: \href{https://doi.org/10.1038/s41467-019-13469-8}{10.1038/s41467-019-13469-8}\allowbreak.}
	\item  I.A. van Hees, P.J.M. Swinkels, R.G. Fokkink, A.H. Velders, I.K. Voets, J. van der Gucht \& M. Kamperman. ``Self-assembly of oppositely charged polyelectrolyte block copolymers containing short ther\-mo\-re\-spon\-si\-ve blo\-cks''. In: \textit{Polymer Chemistry}, 10, 3127-3134 (2019). \texttt{DOI: \href{https://doi.org/10.1039/C9PY00250B}{10.1039/C9PY00250B}\allowbreak}.
\end{itemize}
}

%%%%%%%%%%%%%%%%%
% I want to list those publications in the official bibliography as well, so do that below (even though they do not appear in text).
%%%%%%%%%%%%%%%%%
\nocite{swinkelsRevealingPseudorotationRingopening2021,heesSelfassemblyOppositelyCharged2019,gabryelczykHydrogenBondGuidance2019}